A Summery about reasoning with logic

### 2015-10-31 reasoning/summery.tex
added another induction example.

\subparagraph{Definitions}
Natural numbers are all integers bigger than 0.
\[Even(n) = \left\{ \begin{matrix}
	n=0 &\\ 
	Even(n-2)& 
	\end{matrix}
\right \]

>>>>

\subparagraph{Definitions}
Natural numbers are all integers bigger than 0.

\[
Even(n) := \left\{
	\begin{array}{l}
		n= 0 \\
		Even(n-2)
	\end{array}
\right.
\]
\[
Odd(n) := \left\{
	\begin{array}{l}
		n= 1 \\
		Odd(n-2)
	\end{array}
\right.
\]

\subparagraph{Strategy}
All Natural numbers are either odd or even, this will be proven by induction.

\subparagraph{Proof} \emph{In here we look at the definitions and try to see
the base case(s)}. In case n=0, n is even according to the definition of
even, so n is either postivie or negative. \emph{reflecting back on what
we're trying to prove, saying its the case}

In case n=1, n is odd according to the definition of odd. So n is either
odd or even.

\emph{After the base case, first assume, then push with help of the definition}
Assume n is odd or even, then n+2 is also odd or even according to the
definition of odd or even.

\paragraph{Proof that $\vdash_{gkc} (\Gamma \Rightarrow \Delta)$ is
closed under right weakening}
\emph{I'll treat this one because its a rather simple case, but still
touches the concepts of logic a bit deeper}

\subparagraph{Definitions}
$GKC$ is gentzen calulus. $\vdash_x$ means something is derivable in system x.
We assume $\Gamma \Rightarrow \Delta$ is derivable in $GKC$. This means
there exists an axiom in $\Gamma \Rightarrow \Delta$, for example
$\Gamma', B \Rightarrow B, \Delta'$.
Closed under right weakening means that it doesn't matter if
$\Gamma', B \Rightarrow B, \Delta'$ or $\Gamma', B \Rightarrow B, \Delta', A$
is used since they're both axioms.

\subparagraph{Strategy} To proof for all sequents in $GKC$ right weakening
is closed. To proof with iniduction.
\subparagraph{Proof}
Take an arbitrary proof $P$ that is derivable in $GKC$,
this proof has several sequants $S$ to the depth $n$, such that $S_n = P$.

on depth $n=0$ the sequent is an axiom, because $P$ is derivable in $GKC$.

Assume $P_n$ is closed under right weakening. Then $P_n-1$ is closed under
right weakening to
